---
title: "Errata"
subtitle: "On Coppock (2017), *Statistics, Politics and Policy* 8(1)"
format:
  pdf:
    output-file: coppock_2017a_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

fig <- read_csv(here("maintained", "output", "figure_1_direct_vs_list_estimates.csv"),
                show_col_types = FALSE) |>
  filter(subgroup == "Entire sample")
txt <- read_csv(here("maintained", "output", "text_main_estimates.csv"),
                show_col_types = FALSE)

entire <- function(which, col = "est") fig[[col]][fig$estimator == which]
text_val <- function(label) txt$estimate[txt$quantity == label]

# Entry 5 reads the quintile sizes the rewrite checks on every run, so the note's two
# counts are computed rather than typed.
income <- read_csv(here("maintained", "output", "income_quintile_check.csv"),
                   show_col_types = FALSE)
income_n <- function(q) income$n[income$income_quintile == q]
comma <- function(x) format(x, big.mark = ",", trim = TRUE)
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from this tibble into
# this document and into the machine-readable errata_entries.csv written at the bottom of
# the file, which is what any other document carrying these corrections reads. Before the
# spine existed an entry was written out in prose wherever it was needed, and the copies
# had already diverged.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here. Nothing else in a field is markup, so the same string can be set by any of them.
#
# Numbering is the published note's and is APPEND-ONLY: entry 2 can already have been cited,
# so a later finding is added at the end and never interleaved.
#
# A published or corrected value that the pipeline computes stays computed: the field is
# built with str_glue() so the number is produced when this document renders, not typed.
#
# claim_ids is the semicolon-separated list of ground-truth claim_id values the entry
# corrects, and it is what makes "is this finding published?" a query rather than a reading
# of every note. It is empty where an entry has no ground-truth row, which is normal for a
# bibliographic or structural entry. ground_truth/build_ground_truth.R refuses to build if
# any id here is absent from the ground truth.

# Entry 5's ids, listed here rather than inside the tribble because there are 64 of them:
# the label rotation moves every cell of all five income blocks of Figure 1 and Table A1,
# and each cell is its own ground-truth row. Written out in full, because a pattern that
# selected them would be a rule about names rather than a record of what the entry corrects.
income_label_claim_ids <- c(
  "table_a1_below_20th_income_percentile_direct_est", "table_a1_below_20th_income_percentile_direct_est_se",
  "table_a1_below_20th_income_percentile_list_est", "table_a1_below_20th_income_percentile_list_est_se",
  "table_a1_below_20th_income_percentile_difference", "table_a1_below_20th_income_percentile_difference_se",
  "table_a1_below_20th_income_percentile_direct_est_adj", "table_a1_below_20th_income_percentile_direct_est_adj_se",
  "table_a1_below_20th_income_percentile_list_est_adj", "table_a1_below_20th_income_percentile_list_est_adj_se",
  "table_a1_below_20th_income_percentile_difference_adj", "table_a1_below_20th_income_percentile_difference_adj_se",

  "table_a1_20th40th_income_percentile_direct_est", "table_a1_20th40th_income_percentile_direct_est_se",
  "table_a1_20th40th_income_percentile_list_est", "table_a1_20th40th_income_percentile_list_est_se",
  "table_a1_20th40th_income_percentile_difference", "table_a1_20th40th_income_percentile_difference_se",
  "table_a1_20th40th_income_percentile_direct_est_adj", "table_a1_20th40th_income_percentile_direct_est_adj_se",
  "table_a1_20th40th_income_percentile_list_est_adj", "table_a1_20th40th_income_percentile_list_est_adj_se",
  "table_a1_20th40th_income_percentile_difference_adj", "table_a1_20th40th_income_percentile_difference_adj_se",

  "table_a1_40th60th_income_percentile_direct_est", "table_a1_40th60th_income_percentile_direct_est_se",
  "table_a1_40th60th_income_percentile_list_est", "table_a1_40th60th_income_percentile_list_est_se",
  "table_a1_40th60th_income_percentile_difference", "table_a1_40th60th_income_percentile_difference_se",
  "table_a1_40th60th_income_percentile_direct_est_adj", "table_a1_40th60th_income_percentile_direct_est_adj_se",
  "table_a1_40th60th_income_percentile_list_est_adj", "table_a1_40th60th_income_percentile_list_est_adj_se",
  "table_a1_40th60th_income_percentile_difference_adj", "table_a1_40th60th_income_percentile_difference_adj_se",

  "table_a1_60th80th_income_percentile_direct_est", "table_a1_60th80th_income_percentile_direct_est_se",
  "table_a1_60th80th_income_percentile_list_est", "table_a1_60th80th_income_percentile_list_est_se",
  "table_a1_60th80th_income_percentile_difference", "table_a1_60th80th_income_percentile_difference_se",
  "table_a1_60th80th_income_percentile_direct_est_adj", "table_a1_60th80th_income_percentile_direct_est_adj_se",
  "table_a1_60th80th_income_percentile_list_est_adj", "table_a1_60th80th_income_percentile_list_est_adj_se",
  "table_a1_60th80th_income_percentile_difference_adj", "table_a1_60th80th_income_percentile_difference_adj_se",

  # The Above 80th block is one short of twelve: its adjusted direct-question standard error
  # is 1.4 under both labellings, so that cell agrees with the page and carries no defect.
  "table_a1_above_80th_income_percentile_direct_est", "table_a1_above_80th_income_percentile_direct_est_se",
  "table_a1_above_80th_income_percentile_list_est", "table_a1_above_80th_income_percentile_list_est_se",
  "table_a1_above_80th_income_percentile_difference", "table_a1_above_80th_income_percentile_difference_se",
  "table_a1_above_80th_income_percentile_direct_est_adj", "table_a1_above_80th_income_percentile_list_est_adj",
  "table_a1_above_80th_income_percentile_list_est_adj_se", "table_a1_above_80th_income_percentile_difference_adj",
  "table_a1_above_80th_income_percentile_difference_adj_se",

  "table_a1_below_20th_income_percentile_n", "table_a1_20th40th_income_percentile_n",
  "table_a1_40th60th_income_percentile_n", "table_a1_60th80th_income_percentile_n",
  "table_a1_above_80th_income_percentile_n"
)

entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "definition", "pipeline", "full",
  "Length of the income scale in Equation 1",
  "published Equation 1",
  "A brief justification of this specification: all variables except for 7-point Party ID and [[22-point]] Income are indicators, so not many modeling choices must be made.",
  str_glue("A brief justification of this specification: all variables except for 7-point Party ID and [[{sprintf('%.0f', text_val('income_points'))}-point]] Income are indicators, so not many modeling choices must be made."),
  str_glue(
    "The deposited income variable takes {sprintf('%.0f', text_val('income_points'))} ",
    "distinct values, 1 through {sprintf('%.0f', text_val('income_points'))}, with every ",
    "value present, and the deposited script enters it as it stands."),
  "results_income_points",

  2, "quantity", "pipeline", "full",
  "Standard error of the difference between the two estimates",
  "published Combined Estimate",
  "The bootstrapped standard error of this difference is [[3.4]] points, indicating that is not statistically significantly different from zero.",
  str_glue("The bootstrapped standard error of this difference is [[{sprintf('%.1f', 100 * entire('Difference', 'se'))}]] points, indicating that is not statistically significantly different from zero."),
  "",
  "results_direct_minus_list_se",

  3, "quantity", "pipeline", "full",
  "Difference between the direct question and the list experiment",
  "published Results",
  "Recall that the direct question estimate of Trump support was 32.5%, for a [[2.9]] percentage points difference.",
  str_glue("Recall that the direct question estimate of Trump support was 32.5%, for a [[{sprintf('%.1f', 100 * entire('Difference'))}]] percentage points difference."),
  str_glue(
    "The published figure is the difference of the two rounded shares. The rounded ",
    "difference is {sprintf('%.1f', 100 * entire('Difference'))}, which is what Table A1 ",
    "reports for the same quantity, so the article disagrees with its own appendix."),
  "results_direct_minus_list",

  4, "quantity", "pipeline", "full",
  "Share reporting other, would not vote, or undecided",
  "published Design",
  "Respondents split 32.5% for Donald Trump and 37.0% for Hillary Clinton, while [[30.5%]] reported that they would vote for other candidates, would not vote, or were still undecided.",
  str_glue("Respondents split 32.5% for Donald Trump and 37.0% for Hillary Clinton, while [[{sprintf('%.1f', 100 * text_val('direct_share_other'))}%]] reported that they would vote for other candidates, would not vote, or were still undecided."),
  str_glue(
    "The published figure is 100 minus the two rounded shares. The three remaining response ",
    "categories carry {sprintf('%.1f', 100 * text_val('direct_share_other'))} per cent of ",
    "the weight."),
  "design_direct_share_other",

  5, "label", "pipeline", "full",
  "The income quintile rows of Figure 1 and Table A1 carry each other's labels",
  "published Figure 1 and Table A1",
  "[[Below 20th income percentile]], [[20th-40th income percentile]], [[40th-60th income percentile]], [[60th-80th income percentile]], [[Above 80th income percentile]]",
  "[[20th-40th income percentile]], [[40th-60th income percentile]], [[60th-80th income percentile]], [[Above 80th income percentile]], [[Below 20th income percentile]]",
  str_glue(
    "The deposited script builds the grouping factor with its levels typed in alphabetical ",
    "order and its labels typed in substantive order, so each income row is printed under ",
    "the label belonging to the group before it and the lowest quintile is printed as the ",
    "highest. Every other block in the same call lines up, because only the income levels ",
    "sort differently under the two orders. The direction is not a matter of interpretation: ",
    "income_quintile is a self-describing character variable whose five categories partition ",
    "the deposited household income measure, and the row the article prints as the bottom ",
    "quintile reports N = {comma(income_n('20th - 40th Income Percentile'))}, which is the ",
    "size of the second quintile; the bottom quintile has ",
    "{comma(income_n('Below 20th Income Percentile'))}.",
    "\n\n",
    "The changed artifact is the five labels alone. No estimate, standard error or sample ",
    "size moves, and no conclusion turns on it: the article's claim about income is that the ",
    "groups did not diverge widely, which holds under either labelling. The maintained ",
    "rewrite prints the labels the data supports, which is why its income rows disagree with ",
    "the published ones in the ground truth."),
  paste(income_label_claim_ids, collapse = ";"),

  6, "note", "reading", "brief",
  "A misspelling in the note to Table A1",
  "published, the note to Table A1",
  "Adjusted [[direction]] question estimates are predictions from a logistic regression.",
  "Adjusted [[direct]] question estimates are predictions from a logistic regression.",
  str_glue(
    "The column the note describes is headed Direct question, and every other mention of ",
    "the estimator in the article and in the deposited script spells it that way. The ",
    "misspelling is in the authors' own source as well as on the published page. It was ",
    "found while setting Table A1 for the remastered edition, which reads a float cell by ",
    "cell where the token gate drops its interior on both sides."),
  "",

  7, "wording", "reading", "full",
  "A dropped word in the abstract",
  "published Abstract",
  "A list experiment conducted on the same respondents yields an [[estimate]] 29.6%",
  "A list experiment conducted on the same respondents yields an [[estimate of]] 29.6%",
  str_glue(
    "The word is missing on the published page and in the deposited manuscript. The sentence ",
    "has one reading with it and none without, so what is supplied is recoverable from the ",
    "document rather than chosen for it. Found by reading the abstract against the published ",
    "page while preparing the remastered edition."),
  "",

  8, "wording", "reading", "full",
  "A dropped word in the Combined Estimate section",
  "published Combined Estimate",
  "we should discount the value [[the]] combined estimate",
  "we should discount the value [[of the]] combined estimate",
  str_glue(
    "The same omission as entry 7 and the same reasoning: the sentence is about the value of ",
    "the combined estimate, there is no second reading, and the word is absent from the ",
    "published page rather than from this reading of it."),
  "",

  9, "typography", "reading", "brief",
  "A narrative citation set without its parentheses",
  "published Combined Estimate",
  "Aronow et al. [[2015]] also propose a joint test",
  "Aronow et al. [[(2015)]] also propose a joint test",
  str_glue(
    "Every other narrative citation in the article parenthesises its year: Blair and Imai ",
    "(2012), Glynn (2013), Imai (2011), Dropp (2015). The authors' own source sets this one ",
    "with the same macro as the others, so the parentheses were lost in typesetting."),
  ""
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# Every id an entry claims to correct must be a real ground-truth claim. The build gate in
# ground_truth/build_ground_truth.R checks the same property from the other side; checking it
# here too means a dangling id cannot survive a render.
gt_ids <- read_csv(here("ground_truth", "coppock_2017a_ground_truth.csv"),
                   show_col_types = FALSE)$claim_id
cited_ids <- entries$claim_ids |>
  str_split(";") |>
  unlist() |>
  str_trim() |>
  discard(\(x) is.na(x) | x == "")
stopifnot(all(cited_ids %in% gt_ids))

# The prose below counts the entries in words, as the note has always done.
n_entries_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                    "ten", "eleven", "twelve")[nrow(entries)]

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

This note lists `r n_entries_word` errors in "Did Shy Trump Supporters Bias the 2016 Polls? Evidence from a Nationally-representative List Experiment," published in *Statistics, Politics and Policy* 8(1), doi [10.1515/spp-2016-0005](https://doi.org/10.1515/spp-2016-0005). **None of them changes a conclusion of the paper.** Each is recorded because a reader who took the page at its word would be taking away something the paper's own data do not support. Entries 1 to 4 are misstated numbers: the first two substantive, the next two arising from rounding before subtracting and noted for completeness. Entries 5 and 6 are not numbers at all and are the two that reach a figure and a table rather than a sentence: a set of row labels that carry each other's values, and a misspelling in the note under Table A1.

Every corrected value below is computed from the deposited data at the time this document is rendered. The code and output supporting each correction are at [github.com/active-maintenance-aec/coppock_2017a](https://github.com/active-maintenance-aec/coppock_2017a).

```{r render-entries, results="asis"}
# A heading is only a heading when a blank line precedes it, so every emitted entry opens
# with one.
walk(seq_len(nrow(entries)), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n",
      if (e$note != "") paste0(e$note, "\n") else "", sep = "")
})
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else that
# carries these corrections reads it rather than keeping its own copy, so the two cannot drift.
write_csv(entries, here("errata_entries.csv"))
```
